%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size

\usepackage{tabularx}

\input{structure.tex} % Include the file specifying document layout

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Tanakorn Leesatapornwongsa} % Print the main header

%------------------------------------------------

\parbox{0.4\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{1.5cm} \= \hspace{2cm} \= \kill % Spacing within the block
{\bf Address} \> University of Chicago\\ % Address line 1
\> Department of Computer Science \\ % Address line 2
\> Ryerson Hall, Chicago, IL 60637 \\ % Address line 2
%{\bf Date of Birth} \> 7$^{th}$ September 1979 \\ % Date of birth 
%{\bf Nationality} \> British % Nationality
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.6\textwidth}{ % Second block
\begin{tabbing} % Enables tabbing
\hspace{2.3cm} \= \hspace{2cm} \= \kill % Spacing within the block
{\bf Web} \> \href{http://people.cs.uchicago.edu/\~tanakorn}{http://people.cs.uchicago.edu/\textasciitilde tanakorn} \\ % Web
{\bf Email} \> \href{mailto:tanakorn@cs.uchicago.edu}{tanakorn@cs.uchicago.edu} \\ % Email address
{\bf Office Phone} \> +1 (224) 256 3116 \\ % Office phone
%{\bf Mobile Phone} \> +1 (224) 256 3116 \\ % Mobile phone
\end{tabbing}}

%----------------------------------------------------------------------------------------
%	PERSONAL PROFILE
%----------------------------------------------------------------------------------------

%\section{Personal Profile}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\tabbedblock{
2012 - Present \> \textbf{University of Chicago}, Chicago, IL, USA\\
\>\textit{Ph.D. in Computer Sciences}, expected June 2017\\
\>Advisor: Prof. Haryadi S. Gunawi
}

\tabbedblock{
2012 - 2015 \> \textbf{University of Chicago}, Chicago, IL, USA\\
\>\textit{M.S. in Computer Sciences}\\
\>Advisor: Prof. Haryadi S. Gunawi
}

%------------------------------------------------

\tabbedblock{
2005 - 2009 \> \textbf{Chulalongkorn University}, Bangkok, Thailand\\
\>\textit{B.Eng. in Computer Engineering}
}

%----------------------------------------------------------------------------------------
%	RESEARCH INTERESTS
%----------------------------------------------------------------------------------------

\section{Research Interests}

\begin{tabbing}
\hspace{2.5cm} \= \kill
\textbf{Areas} \> Distributed Systems, Cloud Computing, and Storage Systems. \\
\textbf{Focuses} \> Systems Dependability.
\end{tabbing}

%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------

\section{Work Experiences}

\job{Apr 2013 -}{Present}{Research Assistant}
{University of Chicago, Chicago, IL, USA}
{\begin{minipage}{\smallertextwidth}
Working on \dblquote{\textit{improving the dependability of distributed systems and cloud systems}} topic
with \href{http://ucare.cs.uchicago.edu/}{Prof. Haryadi S. Gunawi}
in \href{http://ucare.cs.uchicago.edu/}{UCARE} Group
\end{minipage}} 

\job{Jun 2016 -}{Aug 2016}{Intern}
{Microsoft Research, Redmond, WA, USA}
{\begin{minipage}{\smallertextwidth}
Worked on \dblquote{\textit{reliability testing for Azure applications}} project,
with \href{https://www.microsoft.com/en-us/research/people/madanm/}{Madan Musuvathi}, 
\href{https://www.microsoft.com/en-us/research/people/sumann/}{Suman Nath}, 
and \href{http://people.csail.mit.edu/lenin/}{Lenin Ravindranath Sivalingam}
\end{minipage}} 

\job{Oct 2015}{}{Guest Lecturer}
{University of Chicago, Chicago, IL, USA}
{Guest lecturer in Advanced Operating Systems course} 

\job{Jun 2014 -}{Aug 2014}{Intern}
{NetApp, Inc., Sunnyvale, CA, USA}
{\begin{minipage}{\smallertextwidth}
Worked on \dblquote{\textit{distributed system scalability checking}} project, 
with Gokul Soundararajan
in \href{http://www.netapp.com/us/company/leadership/advanced-technology/}{Advanced Technology Group (ATG)} 
\end{minipage}}

\job{Oct 2012 -}{Mar 2013}{Teaching Assistant}
{University of Chicago, Chicago, IL, USA}
{TA in Computer Architecture and Mobile Computing courses} 

\job{2009 - 2012}{}{Platform Engineer}
{Wavify Inc., Bangkok, Thailand}
{\begin{minipage}{\smallertextwidth}
\begin{itemize-noindent}
\setlength\itemsep{-1ex}
\item Built P2P data synchronization framework for mobile platform
\item Built file offloading network-attached storage (NAS) for high workload mail server
\end{itemize-noindent}
\end{minipage}}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------

\section{Publications}

\underline{Tanakorn Leesatapornwongsa}, Cesar Stuardo, Huan Ke, Jeffrey F.
Lukman, Riza O. Suminto, Daniar H. Kurniawan, and Haryadi S. Gunawi
\textbf{\textsc{SCk}: Scale-Checking and Debugging Scalability Bugs on One
Machine}. In \textit{preparation}
\vspace{2mm}

Riza O. Suminto, Cesar Stuardo, Alexandra Clark, Huan Ke, \underline{Tanakorn
Leesatapornwongsa}, Bo Fu, Vincentius Martin, Daniar H. Kurniawan, and Haryadi
S. Gunawi \textbf{PBSE: A Robust Path-Based Speculative Execution}. In
\textit{submission to the Proceedings of the USENIX Annual Technical
Conference (ATC)}, 2017
\vspace{2mm}

Haryadi Gunawi, Huan Ke, \underline{Tanakorn Leesatapornwongsa}, Jeffrey
Lukman, Cesar Stuardo, and Riza Suminto
\textbf{Scalability Bugs: When 100-Node Testing is Not Enough}. In
\textit{submission to the Proceedings of the 16th Workshop on Hot Topics in
Operating Systems (HotOS XVI)}, 2017
\vspace{2mm}

\underline{Tanakorn Leesatapornwongsa}, Jeffrey F. Lukman, Shan Lu, and Haryadi
S. Gunawi (the two student authors performed equal work, I was the presenter)
\textbf{TaxDC: A Taxonomy of Non-Deterministic Concurrency Bugs in Datacenter
Distributed Systems}. In \textit{Proceedings of Architectural Support for
Programming Languages and Operating Systems (ASPLOS)}, 2016 
\vspace{2mm}

\underline{Tanakorn Leesatapornwongsa}, and Haryadi S. Gunawi. \textbf{SAMC: A
Fast Model Checker for Finding Heisenbugs in Distributed Systems}. In
\textit{Proceedings of International Symposium on Software Testing and Analysis
(ISSTA)}, 2015
\vspace{2mm}

Haryadi S. Gunawi., Thanh Do, Agung Laksono, Mingzhe Hao, \underline{Tanakorn
Leesatapornwongsa}, Jeffrey F. Lukman, and Riza O. Suminto.  \textbf{What Bugs
Live in the Cloud?: A Study of Issues in Scalable Distributed Systems}. In
\textit{USENIX ;login: Magazine, Vol. 40, No. 4.}, 2015 
\vspace{2mm}

\underline{Tanakorn Leesatapornwongsa}, Mingzhe Hao, Pallavi Joshi, Jeffrey F.
Lukman, and Haryadi S. Gunawi. \textbf{SAMC: Semantic-Aware Model Checking for
Fast Discovery of Deep Bugs in Cloud Systems}. In \textit{Proceedings of the
11th USENIX Symposium on Operating Systems Design and Implementation (OSDI)},
2014
\vspace{2mm}

Haryadi S. Gunawi, Mingzhe Hao, \underline{Tanakorn Leesatapornwongsa}, Tiratat
Patana-anake, Thanh Do, Jeffry Adityatama, Kurnia J. Eliazar, Agung Laksono,
Jeffrey F. Lukman, Vincentius Martin, and Anang D. Satria (Instituitional Order).
\textbf{What Bugs Live in the Cloud? A Study of 3000+ Issues in Cloud Systems}.
In \textit{Proceedings of the 5th ACM Symposium on Cloud Computing (SoCC)}, 2014
\vspace{2mm}

\underline{Tanakorn Leesatapornwongsa} and Haryadi S. Gunawi. \textbf{The Case
for Drill-Ready Cloud Computing}. In \textit{Proceedings of the 5th ACM
Symposium on Cloud Computing (SoCC)}, 2014
\vspace{2mm}

Thanh Do, Mingzhe Hao, \underline{Tanakorn Leesatapornwongsa}, Tiratat
Patana-anake, and Haryadi S. Gunawi (Student Names are in Alphabetical Order).
\textbf{Limplock: Understanding the Impact of Limpware on Scale-Out Cloud
Systems}. In \textit{Proceedings of the 4th ACM Symposium on Cloud Computing
(SoCC)}, 2013

%----------------------------------------------------------------------------------------
%	TALKS SECTION
%----------------------------------------------------------------------------------------

\section{Talks}

\begin{tabbing}
\hspace{2.5cm} \= \kill
Apr 2016 \> \textbf{TaxDC: A Taxonomy of Non-Deterministic Concurrency Bugs in Datacenter Distributed Systems}. \\
\> (ASPLOS '16)
\end{tabbing}

\begin{tabbing}
\hspace{2.5cm} \= \kill
Jul 2015 \> \textbf{SAMC: A Fast Model Checker for Finding Heisenbugs in Distributed System}. (ISSTA '15)
\end{tabbing}

\begin{tabbing}
\hspace{2.5cm} \= \kill
Nov 2014 \> \textbf{The Case for Drill-Ready Cloud Computing}. (SoCC '14)
\end{tabbing}

\begin{tabbing}
\hspace{2.5cm} \= \kill
Oct 2014 \> \textbf{SAMC: Semantic-Aware Model Checking for Fast Discovery of Deep Bugs in Cloud Systems}. \\
\> (OSDI '14)
\end{tabbing}

%----------------------------------------------------------------------------------------
%	POSTER SECTION
%----------------------------------------------------------------------------------------

\section{Posters}

\underline{Tanakorn Leesatapornwongsa,} Cesar Stuardo, Huan Ke, Jeffrey F.
Lukman, Riza O. Suminto, Daniar H. Kurniawan, Haryadi S. Gunawi
\textbf{\textsc{SCk}: Scale-Checking and Debugging Scalability Bugs on One
Machine }. In \textit{Poster Session of the 12th USENIX Symposium on Operating
Systems Design and Implementation (OSDI)}, 2016
\vspace{2mm}

\underline{Tanakorn Leesatapornwongsa,} Jeffrey F. Lukman, Shan Lu, and Haryadi
S. Gunawi. \textbf{TaxDC: A Taxonomy of Non-Deterministic Concurrency Bugs in
Datacenter Distributed Systems}. In \textit{Poster Session of Architectural
Support for Programming Languages and Operating Systems (ASPLOS)}, 2016
\vspace{2mm}

Haryadi S. Gunawi, Mingzhe Hao, \underline{Tanakorn Leesatapornwongsa}, Tiratat
Patana-anake, Thanh Do, Jeffry Adityatama, Kurnia J. Eliazar, Agung Laksono,
Jeffrey F. Lukman, Vincentius Martin, and Anang D. Satria. \textbf{What Bugs
Live in the Cloud? A Study of 3000+ Issues in Cloud Systems}. In
\textit{Poster Session of the 5th ACM Symposium on Cloud Computing (SoCC)}, 2014
\vspace{2mm}

\underline{Tanakorn Leesatapornwongsa,} and Haryadi S. Gunawi. \textbf{The Case
for Drill-Ready Cloud Computing}. In \textit{Poster Session of the 5th ACM
Symposium on Cloud Computing (SoCC)}, 2014
\vspace{2mm}

\underline{Tanakorn Leesatapornwongsa,} Mingzhe Hao, Pallavi Joshi, Jeffrey F.
Lukman, and Haryadi S. Gunawi. \textbf{SAMC: Semantic-Aware Model Checking for
Fast Discovery of Deep Bugs in Cloud Systems}. In \textit{Poster Session of the
11th USENIX Symposium on Operating Systems Design and Implementation (OSDI)},
2014
\vspace{2mm}

Thanh Do, Mingzhe Hao, \underline{Tanakorn Leesatapornwongsa}, Tiratat
Patana-anake, and Haryadi S. Gunawi. \textbf{Limplock: Understanding the Impact
of Limpware on Scale-Out Cloud Systems}. In \textit{Poster Session of the 4th ACM
Symposium on Cloud Computing (SoCC)}, 2013

%----------------------------------------------------------------------------------------
%	AWARD SECTION
%----------------------------------------------------------------------------------------

\section{Awards and Honors}

\begin{tabbing}
\hspace{2.5cm} \= \kill
2016 \> \textbf{2016 - 2017 Facebook Fellowship Finalist}, Facebook
\end{tabbing}

\begin{tabbing}
\hspace{2.5cm} \= \kill
2015 \> \textbf{ISSTA '15 Student Financial Support}, US National Science Foundation (NSF)
\end{tabbing}

\begin{tabbing}
\hspace{2.5cm} \= \kill
2014 \> \textbf{SoCC '14 Student Scholarship}, Association for Computing Machinery (ACM)
\end{tabbing}

\begin{tabbing}
\hspace{2.5cm} \= \kill
2014 \> \textbf{OSDI '14 Student Grant}, USENIX
\end{tabbing}

\begin{tabbing}
\hspace{2.5cm} \= \kill
2014 \> \textbf{UU Fellowship}, University of Chicago
\end{tabbing}

\begin{tabbing}
\hspace{2.5cm} \= \kill
2009 \> \textbf{2nd Class Honor}, Computer Engineering Department, Chulalongkorn University
\end{tabbing}

\begin{tabbing}
\hspace{2.5cm} \= \kill
2008 \> \textbf{1st Place World RoboCup Championship}, RoboCup Soccer Small Size League
\end{tabbing}

%----------------------------------------------------------------------------------------
%	PROJECT SECTION
%----------------------------------------------------------------------------------------

\section{Projects}
\vspace{-4mm}
{\footnotesize Please click on the titles for the reports or more information}

\subsection{Research Projects}

\begin{tabbing}
\hspace{2.5cm} \= \kill
2014 - 2016 \>\+ \textbf{\textsc{SCk}: Scale-Checking and Debugging Scalability Bugs on One Machine} (In submission) \\
\begin{minipage}{\smallertextwidth}
I present a scale-check methodology that empowers developers to check
scalability of distributed systems implementations and helps them reproduce
and debug scalability bugs economically on one machine. 
\end{minipage}
\end{tabbing}

\begin{tabbing}
\hspace{2.5cm} \= \kill
2016 \>\+ \textbf{PBSE: A Robust Path-Based Speculative Execution} (In preparation) \\
\begin{minipage}{\smallertextwidth}
My colleagues and I studied Speculative Execution implementations of
data-parallel frameworks under limping network interfaces, and reveal their
fundamental loopholes. We present PBSE, a novel robust path-based speculative
execution that can recover from the limping failures.
\end{minipage}
\end{tabbing}

\begin{tabbing}
\hspace{2.5cm} \= \kill
2015 \>\+ \href{http://ucare.cs.uchicago.edu/pdf/asplos16-TaxDC.pdf}{\textbf{TaxDC: A Comprehensive Taxonomy of Heisenbugs in Cloud Distributed Systems}} (\textit{ASPLOS '16}) \\
\begin{minipage}{\smallertextwidth}
I as one of the project leaders, conducted the largest and most comprehensive
study on distributed concurrency bugs from four widely-deployed cloud
systems, Cassandra, Hadoop MapReduce, HBase, and ZooKeeper, and introduced a
complete taxonomy of distributed concurrency bugs in cloud systems.
\end{minipage}
\end{tabbing}

\begin{tabbing}
\hspace{2.5cm} \= \kill
2013 - 2014 \> \href{http://ucare.cs.uchicago.edu/pdf/osdi14-samc.pdf}{\textbf{SAMC: Semantic-Aware Model Checking for Fast Discovery of Deep Bugs in Cloud Systems}} \\
\>\+ (\textit{OSDI '14} and \textit{ISSTA '15}) \\
\begin{minipage}{\smallertextwidth}
I introduced semantic-aware model checker, a white-box model checker that takes
semantic knowledge of the target system and incorporates the knowledge into
model checker for distributed systems to speed up the time to unearth
concurrency bugs.
\end{minipage}
\end{tabbing}

\begin{tabbing}
\hspace{2.5cm} \= \kill
2014 \>\+ \href{http://ucare.cs.uchicago.edu/pdf/socc14-drill.pdf}{\textbf{The Case for Drill-Ready Cloud Computing}} (\textit{SoCC '14}) \\
\begin{minipage}{\smallertextwidth}
I explored the fundamental question: \dblquote{\textit{how can we ensure that
cloud services work robustly against many failure scenarios in real
deployments?}}, and proposed a vision of a new reliability paradigm, the
Drill-Ready Cloud Computing, an online testing framework that provides safety,
efficiency, usability, and generality.
\end{minipage}
\end{tabbing}

\begin{tabbing}
\hspace{2.5cm} \= \kill
2013 - 2014 \>\+ \href{http://ucare.cs.uchicago.edu/pdf/socc14-cbs.pdf}{\textbf{What Bugs Live in the Cloud? A Study of 3000+ Issues in Cloud Systems}} (\textit{SoCC '14}) \\
\begin{minipage}{\smallertextwidth}
My colleagues and I comprehensively studied the issues in development and
deployment of six popular cloud-scale distributed systems, Hadoop MapReduce,
HDFS, HBase, Cassandra, ZooKeeper and Flume. This is the largest bug study for
cloud-scale systems (3,655 issues).
\end{minipage}
\end{tabbing}

\begin{tabbing}
\hspace{2.5cm} \= \kill
2013 \>\+ \href{http://ucare.cs.uchicago.edu/pdf/socc13-limplock.pdf}{\textbf{Limplock: Understanding the Impact of Limpware on Scale-Out Cloud Systems}} (\textit{SoCC 2013}) \\
%\>\+ (\textit{SoCC 2013}) \\
\begin{minipage}{\smallertextwidth}
My colleagues and I studied one often-overlooked cause of performance failure:
``\textit{limpware}'', limping hardware whose performance degrades significantly
compares to its specification. The study showed impacts of limpware on
five cloud systems, Cassandra, Hadoop, HBase, HDFS, and ZooKeeper. 
\end{minipage}
\end{tabbing}

\subsection{Industry Projects}

\begin{tabbing}
\hspace{2.5cm} \= \kill
2011 - 2012 \>\+ \textbf{Crossweaver: Data Synchronization Framework for Mobile Platform} (\textit{Wavify Inc.}) \\
\begin{minipage}{\smallertextwidth}
I developed a P2P framework for mobile applications to synchronize data with
each other with the notion of versioning and access control, or synchronize
back to Wavify NextStor, Wavify's cloud storage, for backup.
\end{minipage}
\end{tabbing}

\begin{tabbing}
\hspace{2.5cm} \= \kill
2010 - 2011 \>\+ \textbf{Wavify NextStor} (\textit{Wavify Inc.}) \\
\begin{minipage}{\smallertextwidth}
I built a cloud storage appliance for offloading users' files from Wavify's
mail server product. 
\end{minipage}
\end{tabbing}

%----------------------------------------------------------------------------------------
%	SERVICES SECTION
%----------------------------------------------------------------------------------------

\section{Professional Service}

\begin{tabbing}
\hspace{2.5cm} \= \hspace{3.5cm}  \= \kill
2016 \> \textbf{External reviewer} \> \textit{TCC '16}, IEEE Transactions on Cloud Computing \\
2015 \> \textbf{External reviewer} \> \textit{FAST '16}, USENIX Conference on File and Storage Technologies
\end{tabbing}

%----------------------------------------------------------------------------------------
%	ADVISING SECTION
%----------------------------------------------------------------------------------------

\section{Advising}

I co-advise the following students along with my advisor. I meet with them
every week to direct them in research. Some are students in Univeristy at
Chicago, and some are remote students in Indonesia.
\begin{tabbing}
\hspace{3.5cm} \= \hspace{2.5cm} \= \kill
\textbf{UChicago PhD} \> (3 students) \> Jeffrey F. Lukman, Huan Ke, and Cesar Studardo\\
\textbf{UChicago Masters} \> (3 students) \> Bo Fu, Murphy Zhang, and Yanzhe Wu\\
\textbf{Remote Students} \> (4 students) \> Dikaimin Simon (Surya University),\\
\> \>Danial Heri Kurniawan and Satria Priambada (Bandung Institute of Technology)\\
\> \>Khoirul Hasin (Sepuluh Nopember Institute of Technology)
\end{tabbing}

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILL SECTION
%----------------------------------------------------------------------------------------

\section{Technical Skills}

\begin{tabbing}
\hspace{4cm} \= \kill
\textbf{Operating Systems} \> FreeBSD, Linux \\
\textbf{Distributed Systems} \> Hadoop, ZooKeeper, Cassandra \\
\textbf{File/Storage Systems} \> ext3, RAID, HDFS, QFS, Azure Storage, Cleversafe Storage Cluster\\
\textbf{Programming} \> Java, Python, C/C++, C\texttt{\#}
\end{tabbing}

\end{document}
